Tabular Constraint Learning

### 2016-12-19 Paper/response_letter/response_letter.tex

We have elaborated the differences between TaCLe and FlashFill in the related work section (highlighted in \textcolor{red}{red}), also indicating why FlashFill cannot be applied to the examples we consider. Let us summarize the key differences here \sergey{Samuel, you had a point on this, can you add it ?}:
\begin{itemize}
  \item FlashFill works only with a single table, while TaCLe can handle multiple tables
  \item FlashFill only searches for a string transformation program, while TaCLe works with textual and numeric constraints
  \item FlashFill requires marked input-output columns (and columns are treated as vectors), while TaCLe is unsupervised and works across columns and rows
  \item \sergey{here should be the point by Samuel} like they produce a single program with a single solution, while we enumerate multiple constraints that hold in the data
\end{itemize}

Also, we have compared TaCLe with a baseline: one where the graph dependency is disabled and another where we disabled Step 1 (candidate generation based on properties) and graph dependency. \sergey{Samuel, Tias -- can you expand and correct this one?}

\section{Detailed comments}

\paragraph{Reviewer \#2, point B:How the data was obtained and its detailed overview}
We have extended the description of the gathered collection of spreadsheets in the paper (Section 5.3), also we provided an extensive technical description of the dataset in the corresponding github repository: \url{https://github.com/SergeyParamonov/tacle} and added a table indicating present constraints by category into the Appendix together with description of spreadsheet sources. Let us present the overview here as well: there are three main sources for spreadsheets we have collected.
\begin{itemize}
  \item After identification of popular Excel functions (the MS Office web page has an overview of popular functions), we have searched for online tutorials about these functions and collected them under the category \textbf{Tutorials} (a link to each webpage found and used is provided in the accompanying github repository).
  \item We have collected the exercises under the category \textbf{Exercises} from the introductory Excel book \cite{excel_book} that focused on popular Excel functions.
  \item We have collected under the category \textbf{Data} publicly available economic and crime reporting data from the U.S. Bureau of Economic Analysis (BEA) and U.S. FBI Uniform Crime Reporting (UCR) Program (the links are also provided in the accompanying github repository).
\end{itemize}

The overview of constraint distributions per category is presented in Table \ref{tab:constraint_by_category}.
\begin{table}
  \centering
  \rowcolors{2}{gray!25}{white}
  \caption{Constraint occurrence by category}
  \label{tab:constraint_by_category}
  \begin{tabular}{l | c c c }
    \textbf{Constraint} & \textbf{Exercises} & \textbf{Data} & \textbf{Tutorials}  \\\hline
    average (col) & 0 & 0 & 2 \\
    average (row) & 0 & 1 & 0 \\
    average-if    & 1 & 0 & 0 \\
    count (col) & 0 & 0 & 1 \\
    count-if & 1 & 0 & 0 \\
    difference & 2 & 1 & 0 \\
    equal & 0 & 0 & 10 \\
    foreign-product & 1 & 0 & 0 \\
    fuzzy-lookup & 2 & 0 & 1 \\
    lookup & 1 & 0 & 0 \\
    max (col) & 0 & 0 & 2 \\
    max-if & 1 & 0 & 0 \\
    min (col) & 0 & 0 & 3 \\
    min-if & 1 & 0 & 0 \\
    percentual-diff & 5 & 1 & 0 \\
    product & 2 & 0 & 3 \\
    project & 1 & 0 & 0 \\
    rank & 1 & 0 & 0 \\
    series & 2 & 1 & 0 \\
    sum (col) & 5 & 0 & 10 \\
    sum (row) & 2 & 2 & 3 \\
    sum-if & 2 & 0 & 9 \\
    sum-product & 0 & 0 & 2 \\
  \end{tabular}
\end{table}

\sergey{Samuel, can you have a look at what I wrote in the appendix and in the README and expand it?}

\textbf{Reviwer \#2, point C}:  \textit{According to my understanding, the proposed method exploits possible dependencies and redundancies that may exist between the different constraints. However, it is unclear how such dependencies/redundancies are found. Are they assumed to be given as input? Are they detected by the algorithm? What would be the performance (runtime and precision/recall) of the algorithm if no dependencies/redundancies exist?}

\sergey{Samuel? I guess, we have to say that it should be specified in the constraint itself, on what it depends, kind of given}~

Also, we have evaluated the influence on the runtime of the presence of the dependent graph by disabling it in the system and comparing the results on the datasets and synthetic data as presented in \sergey{Samuel, could you put a ref to where the baseline experiment is?}. There is no difference in the precision/recall, since the dependency graph only allows to avoid checking constraints that are guaranteed to fail, i.e., without the dependency graph the system would have to check the constraints that will fail to establish that indeed they do not hold.

\paragraph{Review \#3, major drawback of the method: sensitivity to the noise}
In the field of Inductive Logic Programming and Constraint Learning, there has been a line of work devoted to noise handling. Let us briefly overview the key methods applicable in our case:
\begin{itemize}
  \item \textbf{Noisy semantics}: a possible approach is to modify the semantics of constraints such as $\sum_{i=1}^n b_i = c$ into $|\sum_{i=1}^n b_i - c| \leq \epsilon$, where $\epsilon$ is the noise level that might be dependent on $b_i$'s, $n$ or $c$.
  \item \textbf{Skip semantics}: another possibility is to allow skipping of elements in vectors, i.e. in the constraint  $\sum_{i=1}^n b_i = c$, we can allow $i$ to skip up to $k$ elements to match $c$, then we treat skipped values as noise and do not take them into account.
  \item \textbf{Soft constraints}: a constraint satisfaction is determined by a real-value measure such as $|\sum_{i=1}^n b_i - c | = \sigma|c|$, where $\sigma=0$ denotes the perfect match and the other values denote deviations in absolute values of $c$, then our goal would be to select top-$k$ best matching constraints according to the designed measure.
\end{itemize}

@@

\paragraph{Review \#3, major drawback of the method: sensitivity to the noise}
In the field of Inductive Logic Programming and Constraint Learning, there has been a line of work devoted to noise handling. Let us briefly overview the key methods applicable in our case:
\begin{itemize}
  \item \textbf{Noisy semantics}: a possible approach is to modify the semantics of constraints such as $\sum_{i=1}^n b_i = c$ into $|\sum_{i=1}^n b_i - c| \leq \epsilon$, where $\epsilon$ is the noise level that might be dependent on $b_i$'s, $n$ or $c$.
  \item \textbf{Skip semantics}: another possibility is to allow skipping of elements in vectors, i.e. in the constraint  $\sum_{i=1}^n b_i = c$, we can allow $i$ to skip up to $k$ elements to match $c$, then we treat skipped values as noise and do not take them into account.
  \item \textbf{Soft constraints}: a constraint satisfaction is determined by a real-value measure such as $|\sum_{i=1}^n b_i - c | = \sigma|c|$, where $\sigma=0$ denotes the perfect match and the other values denote deviations in absolute values of $c$, then our goal would be to select top-$k$ best matching constraints according to the designed measure.
\end{itemize}

We have expanded the conclusions section to accommodate these proposals.

\paragraph{Reviewer \#3, (non)-contiguous blocks} \textit{
The requirement that blocks are contiguous makes sense, but also feels like a severe limitation. Please explain more clearly why this is (not) the case.}
\sergey{Samuel, we have a short discussion that it breaks everything, right? Like you cannot prune, for example and also that skip semantics kind of imitates non-contiguous blocks}

\bibliography{references}
\end{document}
